Potential and limits of site-specific substitution model inference.

### 2019-12-30 manuscript/ms.tex
corrected github link

In total, this amounts to 80 alignments for each of the data set sizes $n=100,300,1000,3000$ and four different ensembles.
For each alignment, we reconstructed phylogenetic trees using IQ-tree \citep{nguyen_iq-tree:_2015} with a GTR+R10 model or FastTree \citep{FastTree} using the default 20 category model for nucleotide and amino-acid sequences, respectively.
These trees were used to infer site specific models from data, see below.
The exact workflow is documented in the script \texttt{src/generate\_toy\_data.py} in the associated git repository at \href{https://github.org/neherlab/SiteSpecificGTR}{github.org/neherlab/SiteSpecificGTR}.

\subsection*{Model inference from simulated data}
Simulated data and trees (reconstructed or true) were read in by TreeTime and models reconstructed using functions of TreeTime to infer models with the different approximations discussed in the text.
The exact workflow is documented in the script \texttt{src/reconstruct\_toy\_data.py} in the associated git repository at \href{https://github.org/neherlab/SiteSpecificGTR}{github.org/neherlab/SiteSpecificGTR}.

@@

The sequences and trees were then used for site specific GTR inference as implemented in TreeTime \citep{sagulenko2017treetime}.
The scripts detailing this analysis and producing the figures are available on GitHub in repository \href{https://github.com/neherlab/SiteSpecificGTR}{neherlab/SiteSpecificGTR}.

>>>>

In total, this amounts to 80 alignments for each of the data set sizes $n=100,300,1000,3000$ and four different ensembles.
For each alignment, we reconstructed phylogenetic trees using IQ-tree \citep{nguyen_iq-tree:_2015} with a GTR+R10 model or FastTree \citep{FastTree} using the default 20 category model for nucleotide and amino-acid sequences, respectively.
These trees were used to infer site specific models from data, see below.
The exact workflow is documented in the script \texttt{src/generate\_toy\_data.py} in the associated git repository at \href{https://github.com/neherlab/2019_Puller_SiteSpecificGTR}{github.org/neherlab/2019\_Puller\_SiteSpecificGTR}.

\subsection*{Model inference from simulated data}
Simulated data and trees (reconstructed or true) were read in by TreeTime and models reconstructed using functions of TreeTime to infer models with the different approximations discussed in the text.
The exact workflow is documented in the script \texttt{src/reconstruct\_toy\_data.py} in the associated git repository at \href{https://github.com/neherlab/2019_Puller_SiteSpecificGTR}{github.org/neherlab/2019\_Puller\_SiteSpecificGTR}.

@@

The sequences and trees were then used for site specific GTR inference as implemented in TreeTime \citep{sagulenko2017treetime}.
The scripts detailing this analysis and producing the figures are available on GitHub in repository \url{https://github.com/neherlab/2019_Puller_SiteSpecificGTR}{github.org/neherlab/2019\_Puller\_SiteSpecificGTR}.
